### 2021-07-26 MSA_Notum_journey.Rmd
MSA_Notum_journey init commit

---
title: "The journey of Multiple Sequence Alignment"
subtitle: "Diving in the Notum"
author: "Constantinos Yeles (Konstantinos Geles)"
date: "First version: Tue 26/07/2021, Latest update: `r format(Sys.time(), '%a %d/%b/%Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
  html_document:
    toc: yes
    toc_depth: 3
    theme: paper 
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Blast alignment
First we need to download the fasta sequence and the database from
dropbox? Maybe can be uploaded later to zenodo 
(probably I will have more context to add later).

We will use local blast run on docker as the [link](https://faculty.virginia.edu/wrpearson/fasta/) wasn't working.

```{bash}
# get the docker and run
docker pull ncbi/blast
docker run --rm -ti -v $(pwd):/home/my_data  ncbi/blast
# move inside /home dir of the container
cd /home

# create a folder for the ouput of the blast database and unzip the fasta sequences
mkdir my_data/some_species_blast_db
gunzip my_data/oma_db.gz

# make a blast database 
makeblastdb  -dbtype "prot" -in "my_data/oma_db" -input_type "fasta" -out "my_data/some_species_blast_db/blast_oma.db" -logfile "my_data/some_species_blast_db/logfile"

# blast the sequence of Notum
blastp -query "my_data/dm_notum.fasta"  -db "my_data/some_species_blast_db/blast_oma.db" -out "my_data/results_blast.txt" -outfmt "7 delim=@ qseqid qlen sseqid slen qstart qend sstart send qseq sseq evalue bitscore score length pident nident mismatch positive ppos frames qframe sframe sstrand qcovs qcovhsp qcovus" -num_threads 4
```

# Import results into R
```{r include=FALSE, eval = TRUE}
# load libraries
suppressPackageStartupMessages({
library(tidyverse)
library(plyranges)
library(vroom)
  })

# function to import the results
read_blast_tab_format <- function(blast_file, delim = "@"){
  fourth_line_fields <- blast_file %>% 
  vroom_lines() %>% 
  .[4] %>% 
  str_remove("# Fields: ") %>% 
  str_split(", ") %>% 
  unlist %>% 
  str_replace_all(" |/","_") %>% 
  str_replace("%","percent") %>% 
  str_remove("\\.")

  blast_sequences <- blast_file %>% 
  read_delim(delim = delim, # here it should be made clear that the delim could be something else
             comment = "#", 
             col_names = fourth_line_fields) %>% 
  mutate(strand = ifelse(subject_strand == "minus","-","+") %>% as_factor()) %>% 
  mutate(
         start = ifelse(strand == "-", yes = s_end, no = s_start),
         end = ifelse(strand == "-", yes = s_start,no = s_end),
         seqnames = subject_id) %>% 
    as_granges()

  return(blast_sequences)
}
# import the results

notum_blst <- read_blast_tab_format(blast_file = "results_blast.txt")
```

# print an example of the results 
```{r eval = TRUE}
notum_blst %>% arrange(evalue)
```

# get the 10 top hits identifiers
```{r eval = TRUE}
top10_seqs <- notum_blst %>% arrange(evalue) %>% head(11) %>%  .$subject_id
```

# import fasta db
import the sequences and filter them for the 10 best hits from the previous results in order to make the multiple sequence alignments
```{r eval = TRUE}
suppressPackageStartupMessages({
library(Biostrings)
  })
fasta_db <- readAAStringSet("oma_db")

# I didn't consider that the names will be cut in the db creation thus I have to manipulate them to work properly for the filtering
names_fst_db <- fasta_db  %>% names %>% str_remove(" .+")

# filter for the top 10
fasta_db_fil <- fasta_db[names_fst_db %in% top10_seqs]
```

# Multiple Sequence Alignment
I found two packages in R implementing various algorithms. 
One is [msa](https://www.bioconductor.org/packages/release/bioc/html/msa.html) and the other [DECIPHER](https://www.bioconductor.org/packages/release/bioc/html/DECIPHER.html)
for now I will try msa
```{r eval = TRUE}
suppressPackageStartupMessages({
library(msa)
  })
myFirstAlignment <- msa(fasta_db_fil)
```

# print the MSA
```{r eval = TRUE}
myFirstAlignment
```

### 2021-07-27 MSA_Notum_journey.Rmd
add the full msa output

@@
 output:
-  pdf_document:
-    toc: yes
-    toc_depth: 3
   html_document:
@@
     theme: paper 
+  pdf_document:
+    toc: yes
+    toc_depth: 3
 editor_options:
@@
 ```{r eval = TRUE}
-myFirstAlignment
+print(myFirstAlignment, show="complete")
 ```

### 2021-07-27 MSA_Notum_journey.Rmd
add msa with muscle

@@
 library(msa)
+library(bios2mds)
   })
@@
 ```
+
+# get significant sequences
+```{r eval = TRUE}
+sign_seqs <- notum_blst %>% filter(evalue < 0.05) %>% .$subject_id
+
+# filter for the significant sequences
+fasta_db_fil <- fasta_db[names_fst_db %in% sign_seqs]
+```
+
+# perform MSA with MUSCLE
+```{r}
+sign_seqs_muscle <- msaMuscle(fasta_db_fil)
+sign_seqs_bio2mds <- msa::msaConvert(sign_seqs_muscle, type = "bios2mds::align")
+export.fasta(sign_seqs_bio2mds, outfile = "sign_seqs_msa_muscle.fa", ncol = 60, open = "w")
+```
+check the sign_seqs_msa_muscle.fa file for the alignments

### 2021-07-28 MSA_Notum_journey.Rmd
add iqtree and iqtree results with MUSCLE msa

@@
 
-# print an example of the results 
+## print an example of the results 
 ```{r eval = TRUE}
@@
 
-# get the 10 top hits identifiers
+## get the 10 top hits identifiers
 ```{r eval = TRUE}
@@
 
-# import fasta db
+## import fasta file with all sequences
 import the sequences and filter them for the 10 best hits from the previous results in order to make the multiple sequence alignments
@@
 
-# print the MSA
+## print the MSA
 ```{r eval = TRUE}
@@
 
-# get significant sequences
+## get significant sequences
 ```{r eval = TRUE}
@@
 
-# perform MSA with MUSCLE
+## perform MSA with MUSCLE
 ```{r}
@@
 check the sign_seqs_msa_muscle.fa file for the alignments
+
+# IQTREE
+```{bash}
+docker run --rm -ti -v $(pwd):/home/my_data staphb/iqtree
+
+cd home
+mkdir my_data/my_first_tree
+
+iqtree -s my_data/sign_seqs_msa_muscle.fa -nt 6 -mset LG -pre my_data/my_first_tree/my_tree
+
+```

### 2021-07-29 MSA_Notum_journey.Rmd
add hmmsearch of NOTUM

@@
 ```
+
+# Following the "Estimating phylogenetic trees with phangorn"
+```{r}
+library(ape)
+library(phangorn)
+```
+## Distance based methods
+
+### UPGMA
+```{r}
+sign_seqs_phyDat <- as.phyDat(sign_seqs_muscle, type = "AA")
+
+dm  <- dist.ml(sign_seqs_phyDat)
+
+treeUPGMA  <- upgma(dm)
+
+treeNJ  <- NJ(dm)
+
+plot(treeUPGMA, main="UPGMA")
+
+plot(treeNJ, "unrooted", main="NJ")
+```
+
+### Bootstrap
+```{r}
+fun <- function(x) upgma(dist.ml(x))
+
+bs_upgma <- bootstrap.phyDat(sign_seqs_phyDat,  fun)
+
+#bs_upgma <- bootstrap.phyDat(sign_seqs_phyDat,  \(x){dist.ml(x) |> upgma})
+
+plotBS(treeUPGMA, bs_upgma, main="UPGMA")
+```
+
+### Parsimony
+```{r}
+parsimony(treeUPGMA, sign_seqs_phyDat)
+parsimony(treeNJ, sign_seqs_phyDat)
+
+treePars  <- optim.parsimony(treeUPGMA, sign_seqs_phyDat)
+
+#parsimony ratchet (Nixon 1999)
+treeRatchet  <- pratchet(sign_seqs_phyDat, trace = 0)
+parsimony(c(treePars, treeRatchet), sign_seqs_phyDat)
+
+treeRatchet  <- acctran(treeRatchet, sign_seqs_phyDat)
+
+plotBS(midpoint(treeRatchet), type="phylogram")
+```
+
+### Maximum likelihood
+```{r}
+fit = pml(treeNJ, data=sign_seqs_phyDat)
+fit
+fitJC  <- optim.pml(fit, TRUE)
+logLik(fitJC)
+
+fitWAG <- update(fit, k=4, inv=0.2)
+
+fitWAG <- optim.pml(fitWAG, model="Dayhoff_DCMut", optInv=TRUE, optGamma=TRUE,
+    rearrangement = "stochastic", control = pml.control(trace = 0))
+fitGTR
+```
+
+# HMMER
+## hmmsearch
+```{bash}
+docker run --rm -ti -v $(pwd):/home/my_data  staphb/hmmer
+cd ..
+
+mkdir my_data/hmm_search
+
+hmmsearch --cut_ga --domtblout my_data/hmm_search/PAE_domtbl.out my_data/PAE.hmm my_data/oma_db > /dev/null
+```
+
+## Import hmmsearch results into R
+```{r}
+hmmsearch_result <- "hmm_search/PAE_domtbl.out"
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target")
+
+notum_hmmsearch <- data.table::fread(cmd = "grep -v '^#' hmm_search/PAE_domtbl.out", 
+                  header = FALSE, sep = " ",  fill=TRUE) %>% 
+  unite("V23",c(str_c("V",23:33)))
+
+names(notum_hmmsearch) <- second_line_fields
+```
+
+## Multiple Sequence Alignment
+```{r}
+# filter for the hmmsearch complete sequences
+fasta_db_fil <- fasta_db[names_fst_db %in% notum_hmmsearch$target_name]
+
+# filter for the hmmsearch env_coord sequences
+fasta_db_fil_with_len <- fasta_db[names_fst_db %in% notum_hmmsearch$target_name]
+
+fasta_db_fil_with_len <- fasta_db_fil_with_len[sort(names(fasta_db_fil_with_len))]
+
+notum_hmmsearch_clm <- notum_hmmsearch %>% 
+  filter(!duplicated(target_name)) %>% 
+  select(target_name, from_env_coord, to_env_coord) %>% 
+  arrange(target_name)
+
+#fasta_db_fil_with_len %>% head %>% Biostrings::as.list() %>% Biostrings::AAStringSet()
+fasta_db_fil_with_len <- pmap(list(fasta_db_fil_with_len %>% as.list, 
+          notum_hmmsearch_clm %>% select(target_name, from_env_coord) %>% deframe %>% as.list(),
+          notum_hmmsearch_clm %>% select(target_name, to_env_coord) %>% deframe %>% as.list()),
+     subseq) %>% Biostrings::AAStringSet()
+```
+
+## perform MSA with MUSCLE hmmsearch
+```{r}
+hmmsearch_muscle <- msaMuscle(fasta_db_fil)
+hmmsearch_bio2mds <- msa::msaConvert(hmmsearch_muscle, type = "bios2mds::align")
+export.fasta(hmmsearch_bio2mds, outfile = "hmmsearch_msa_muscle.fa", ncol = 60, open = "w")
+
+## env_coord
+hmmsearch_env_coord_muscle <- msaMuscle(fasta_db_fil_with_len)
+hmmsearch_env_coord_bio2mds <- msa::msaConvert(hmmsearch_env_coord_muscle, type = "bios2mds::align")
+export.fasta(hmmsearch_env_coord_bio2mds, outfile = "hmmsearch_env_coord_msa_muscle.fa", ncol = 60, open = "w")
+```
+check the sign_seqs_msa_muscle.fa file for the alignments
+
+## IQTREE hmmsearch
+```{bash}
+docker run --rm -ti -v $(pwd):/home/my_data staphb/iqtree
+
+cd home
+mkdir my_data/my_hmmsearch_tree
+
+iqtree -s my_data/hmmsearch_msa_muscle.fa -nt 8 -mset LG -pre my_data/my_hmmsearch_tree/my_hmmsearch_tree
+
+iqtree -s my_data/hmmsearch_env_coord_msa_muscle.fa -nt 8 -mset LG -pre my_data/my_hmmsearch_tree/my_hmmsearch_env_coord_tree
+
+```

### 2021-07-30 MSA_Notum_journey.Rmd
Add hmm search for WIF and wnt

@@
 cd home
-mkdir my_data/my_hmmsearch_tree
 
@@
 ```
+
+# wnt Family
+## HMMER:hmmsearch
+```{bash}
+docker run --rm -ti -v $(pwd):/home/my_data  staphb/hmmer
+cd ..
+cd home
+
+hmmsearch --cut_ga --domtblout my_data/hmm_search/wnt_domtbl.out my_data/wnt.hmm my_data/oma_db > /dev/null
+```
+
+## Import hmmsearch results into R
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target")
+
+wnt_hmmsearch <- data.table::fread(cmd = "grep -v '^#' hmm_search/wnt_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=23;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(wnt_hmmsearch)[1:23] <- second_line_fields
+```
+
+## Multiple Sequence Alignment
+```{r}
+# filter for the hmmsearch env_coord sequences
+fasta_db_fil_with_len <- fasta_db[names_fst_db %in% wnt_hmmsearch$target_name]
+
+fasta_db_fil_with_len <- fasta_db_fil_with_len[sort(names(fasta_db_fil_with_len))]
+
+wnt_hmmsearch <- wnt_hmmsearch %>% 
+  filter(!duplicated(target_name)) %>% 
+  select(target_name, from_env_coord, to_env_coord) %>% 
+  arrange(target_name)
+
+#fasta_db_fil_with_len %>% head %>% Biostrings::as.list() %>% Biostrings::AAStringSet()
+fasta_db_fil_with_len <- pmap(list(fasta_db_fil_with_len %>% as.list, 
+          wnt_hmmsearch %>% select(target_name, from_env_coord) %>% deframe %>% as.list(),
+          wnt_hmmsearch %>% select(target_name, to_env_coord) %>% deframe %>% as.list()),
+     subseq) %>% Biostrings::AAStringSet()
+```
+
+## perform MSA with MUSCLE hmmsearch
+```{r}
+## env_coord
+hmmsearch_env_coord_muscle <- msaMuscle(fasta_db_fil_with_len)
+hmmsearch_env_coord_bio2mds <- msa::msaConvert(hmmsearch_env_coord_muscle, type = "bios2mds::align")
+export.fasta(hmmsearch_env_coord_bio2mds, outfile = "wnt_hmmsearch_env_coord_msa_muscle.fa", ncol = 60, open = "w")
+```
+check the sign_seqs_msa_muscle.fa file for the alignments
+
+## IQTREE hmmsearch
+```{bash}
+docker run --rm -ti -v $(pwd):/home/my_data staphb/iqtree
+
+cd home
+
+iqtree -s my_data/wnt_hmmsearch_env_coord_msa_muscle.fa -nt 8 -mset LG -pre my_data/my_hmmsearch_tree/wnt_hmmsearch_env_coord_tree
+
+```
+
+# WIF Family
+## HMMER:hmmsearch
+```{bash}
+docker run --rm -ti -v $(pwd):/home/my_data  staphb/hmmer
+
+cd home
+
+hmmsearch --cut_ga --domtblout my_data/hmm_search/WIF_domtbl.out my_data/WIF.hmm my_data/oma_db > /dev/null
+```
+
+## Import hmmsearch results into R
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target")
+
+WIF_hmmsearch <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=23;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_hmmsearch)[1:23] <- second_line_fields
+```
+
+## Multiple Sequence Alignment
+```{r}
+# filter for the hmmsearch env_coord sequences
+fasta_db_fil_with_len <- fasta_db[names_fst_db %in% WIF_hmmsearch$target_name]
+
+fasta_db_fil_with_len <- fasta_db_fil_with_len[sort(names(fasta_db_fil_with_len))]
+
+WIF_hmmsearch <- WIF_hmmsearch %>% 
+  filter(!duplicated(target_name)) %>% 
+  select(target_name, from_env_coord, to_env_coord) %>% 
+  arrange(target_name)
+
+identical(fasta_db_fil_with_len %>% names %>% str_remove(" .+"),
+          WIF_hmmsearch$target_name)
+
+#fasta_db_fil_with_len %>% head %>% Biostrings::as.list() %>% Biostrings::AAStringSet()
+fasta_db_fil_with_len <- pmap(list(fasta_db_fil_with_len %>% as.list, 
+          WIF_hmmsearch %>% select(target_name, from_env_coord) %>% deframe %>% as.list(),
+          WIF_hmmsearch %>% select(target_name, to_env_coord) %>% deframe %>% as.list()),
+     subseq) %>% Biostrings::AAStringSet()
+```
+
+## perform MSA with MUSCLE hmmsearch
+```{r}
+## env_coord
+hmmsearch_env_coord_muscle <- msaMuscle(fasta_db_fil_with_len, type = "protein")
+hmmsearch_env_coord_bio2mds <- msa::msaConvert(hmmsearch_env_coord_muscle, type = "bios2mds::align")
+export.fasta(hmmsearch_env_coord_bio2mds, outfile = "WIF_hmmsearch_env_coord_msa_muscle.fa", ncol = 60, open = "w")
+```
+check the sign_seqs_msa_muscle.fa file for the alignments
+
+## IQTREE hmmsearch
+```{bash}
+docker run --rm -ti -v $(pwd):/home/my_data staphb/iqtree
+
+cd home
+
+iqtree -s my_data/WIF_hmmsearch_env_coord_msa_muscle.fa -nt 4 -mset LG -pre my_data/my_hmmsearch_tree/WIF_hmmsearch_env_coord_tree
+
+```

### 2021-08-02 MSA_Notum_journey.Rmd
Hs PORCN porcupine

@@
 fasta_db <- readAAStringSet("oma_db")
+fasta_db <- fasta_db[sort(names(fasta_db))]
 
@@
 
-# WIF Family
+# Searching for the Hs PORCN, protein-cysteine N-palmitoyltransferase porcupine isoform X5 [Homo sapiens]
+## the Fasta file
+```{bash}
+cat porcn_hs.fasta 
+>Hs|PORCN  gi|530421517|ref|XP_005272694.1| gi|530421517|ref|XP_005272694.1| PREDICTED: protein-cysteine N-palmitoyltransferase porcupine isoform X5 [Homo sapiens]
+MYAIPSPSDWTVHSTGETEVLHSLQVTGCACACRTPTCTQLVAQSDVPDFSRLPPVLQYR
+ASTWAGQPQTEISIHLAIHPWGSAMATFSRQEFFQQLLQGCLLPTAQQGLDQIWLLLAIC
+LACRLLWRLGLPSYLKHASTVAGGFFSLYHFFQLHMVWVVLLSLLCYLVLFLCRHSSHRG
+VFLSVTILIYLLMGEMHMVDTVTWHKMRGAQMIVAMKAVSLGFDLDRGEVGTVPSPVEFM
+GYLYFVGTIVFGPWISFHSYLQAVQGRPLSCRWLQKVARSLALALLCLVLSTCVGPYLFP
+YFIPLNGDRLLRNKKRKARGTMVRWLRAYESAVSFHFSNYFVGFLSEATATLAGAGFTEE
+KDHLEWDLTVSKPLNVELPRSMVEVVTSWNLPMSYWLNNYVFKNALRLGTFSAVLVTYAA
+SALLHGFSFHLAAVLLSLAFITYVEHVLRKRLARILSACVLSKRCPPDCSHQHRLGLGVR
+ALNLLFGALAIFHLAYLGSLFDVDVDDTTEEQGYGMAYTVHKWSELSWASHWVTFGCWIF
+YRLIG
+```
+
+## PFAM search
+we search the sequence on the PFAM site and we get the MBOAT, 
+membrane-bound O-acyltransferase family as result.
+We download the model for the MBOAT
+
 ## HMMER:hmmsearch
@@
 
-cd home
+cd /home
 
-hmmsearch --cut_ga --domtblout my_data/hmm_search/WIF_domtbl.out my_data/WIF.hmm my_data/oma_db > /dev/null
+hmmsearch --cut_ga --domtblout my_data/hmm_search/MBOAT_domtbl.out my_data/MBOAT.hmm my_data/oma_db > /dev/null
 ```
@@
 
-WIF_hmmsearch <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=23;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+MBOAT_hmmsearch <- data.table::fread(cmd = "grep -v '^#' hmm_search/MBOAT_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=23;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
 
-names(WIF_hmmsearch)[1:23] <- second_line_fields
+names(MBOAT_hmmsearch)[1:23] <- second_line_fields
 ```
@@
 # filter for the hmmsearch env_coord sequences
-fasta_db_fil_with_len <- fasta_db[names_fst_db %in% WIF_hmmsearch$target_name]
+fasta_db_fil_with_len <- fasta_db[names_fst_db %in% MBOAT_hmmsearch$target_name]
 
-fasta_db_fil_with_len <- fasta_db_fil_with_len[sort(names(fasta_db_fil_with_len))]
-
-WIF_hmmsearch <- WIF_hmmsearch %>% 
+MBOAT_hmmsearch <- MBOAT_hmmsearch %>% 
   filter(!duplicated(target_name)) %>% 
@@
 identical(fasta_db_fil_with_len %>% names %>% str_remove(" .+"),
-          WIF_hmmsearch$target_name)
+          MBOAT_hmmsearch$target_name)
 
@@
 fasta_db_fil_with_len <- pmap(list(fasta_db_fil_with_len %>% as.list, 
-          WIF_hmmsearch %>% select(target_name, from_env_coord) %>% deframe %>% as.list(),
-          WIF_hmmsearch %>% select(target_name, to_env_coord) %>% deframe %>% as.list()),
+          MBOAT_hmmsearch %>% select(target_name, from_env_coord) %>% deframe %>% as.list(),
+          MBOAT_hmmsearch %>% select(target_name, to_env_coord) %>% deframe %>% as.list()),
      subseq) %>% Biostrings::AAStringSet()
@@
 hmmsearch_env_coord_bio2mds <- msa::msaConvert(hmmsearch_env_coord_muscle, type = "bios2mds::align")
-export.fasta(hmmsearch_env_coord_bio2mds, outfile = "WIF_hmmsearch_env_coord_msa_muscle.fa", ncol = 60, open = "w")
+export.fasta(hmmsearch_env_coord_bio2mds, outfile = "MBOAT_hmmsearch_env_coord_msa_muscle.fa", ncol = 60, open = "w")
 ```
@@
 
-iqtree -s my_data/WIF_hmmsearch_env_coord_msa_muscle.fa -nt 4 -mset LG -pre my_data/my_hmmsearch_tree/WIF_hmmsearch_env_coord_tree
+iqtree -s my_data/MBOAT_hmmsearch_env_coord_msa_muscle.fa -nt 4 -mset LG -pre my_data/my_hmmsearch_tree/MBOAT_hmmsearch_env_coord_tree
 
 ```
+
+# hmmmbuild
+```{bash}
+hmmbuild --amino --cpu 4  my_data/NOTUM_try my_data/hmmsearch_env_coord_msa_muscle.fa 
+hmmbuild --amino --cpu 4  my_data/WIF_try my_data/WIF_hmmsearch_env_coord_msa_muscle.fa 
+hmmbuild --amino --cpu 4  my_data/wnt_try my_data/wnt_hmmsearch_env_coord_msa_muscle.fa
+
+```

### 2021-08-02 MSA_Notum_journey.Rmd
search the profile

@@
 
-# hmmmbuild
+# hmmbuild
 ```{bash}
@@
 hmmbuild --amino --cpu 4  my_data/wnt_try my_data/wnt_hmmsearch_env_coord_msa_muscle.fa 
+```
 
+```{bash}
+hmmsearch --cut_ga --domtblout my_data/hmm_search/NOTUM_profile_domtbl.out my_data/NOTUM_try my_data/pfam/Pfam-A.fasta > /dev/null
 ```

### 2021-08-03 MSA_Notum_journey.Rmd
pfam hmmscan for WIF seq

@@
 
+# hmmscan WIF proteins in pfam domains
+## export the WIF sequences from oma.db
+```{r}
+fasta_db_fil_with_len %>% Biostrings::writeXStringSet("WIF_oma_seq.fasta")
+```
+
 ```{bash}
-hmmsearch --cut_ga --domtblout my_data/hmm_search/NOTUM_profile_domtbl.out my_data/NOTUM_try my_data/pfam/Pfam-A.fasta > /dev/null
+hmmpress my_data/pfam/Pfam-A.hmm
+
+hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_domtbl.out my_data/pfam/Pfam-A.hmm my_data/WIF_oma_seq.fasta > /dev/null
+
 ```

### 2021-08-03 MSA_Notum_journey.Rmd
WIF scan results

@@
 ```
+## Import hmmscan results into R
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target_1",
+                        "description_of_target_2","description_of_target_3")
+
+WIF_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_profile_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_hmmscan)[1:25] <- second_line_fields
+```

### 2021-08-04 MSA_Notum_journey.Rmd
find various domains for WIF proteins add results on tree

@@
 names(WIF_hmmscan)[1:25] <- second_line_fields
+
+WIF_hmmscan %>% 
+  distinct(target_name, query_name) %>% 
+  pivot_wider(names_from = target_name, values_from = target_name,values_fill = "0") %>% 
+  unite(col = "domains",2:11) %>% 
+  mutate(domains = domains %>% str_remove_all("0_") %>% str_remove_all("_0"),
+         query_name = query_name %>% str_replace("\\|","_")) %>% 
+  unite(query_name, 1:2, sep = "__DOMAIN__") %>% view()
 ```

### 2021-08-05 MSA_Notum_journey.Rmd
tblastn sequences

@@
 ```
+
+# Search four "representative" proteins that have the WIF domain respect to sponges
+In the tree of WIF from oma.db we can see 4 big clusters that have particular characteristics
+One is the cluster of the Human WIF (HS|WIF1) the the human with RYK domain (Hs|RYK) then those with 
+NTR domain and then those with the "pure"  PK_TYR_SER_THR_PKinase
+We will tblastn from each cluster one and evaluate some of the results
+## The selected sequences:
+
+### Hs|WIF1 
+```{bash}
+>Hs|WIF1 gi|111125011|ref|NP_009122.2| gi|111125011|ref|NP_009122.2| wnt inhibitory factor 1 precursor [Homo sapiens]
+MARRSAFPAAALWLWSILLCLLALRAEAGPPQEESLYLWIDAHQARVLIGFEEDILIVSEGKMAPFTHDFRKAQQRMPAI
+PVNIHSMNFTWQAAGQAEYFYEFLSLRSLDKGIMADPTVNVPLLGTVPHKASVVQVGFPCLGKQDGVAAFEVDVIVMNSE
+GNTILQTPQNAIFFKTCQQAECPGGCRNGGFCNERRICECPDGFHGPHCEKALCTPRCMNGGLCVTPGFCICPPGFYGVN
+CDKANCSTTCFNGGTCFYPGKCICPPGLEGEQCEISKCPQPCRNGGKCIGKSKCKCSKGYQGDLCSKPVCEPGCGAHGTC
+HEPNKCQCQEGWHGRHCNKRYEASLIHALRPAGAQLRQHTPSLKKAEERRDPPESNYIW
+```
+
+### Hs|RYK
+```{bash}
+>Hs|RYK gi|54607020|ref|NP_001005861.1| gi|54607020|ref|NP_001005861.1| tyrosine-protein kinase RYK isoform 1 precursor [Homo sapiens]
+MRGAARLGRPGRSCLPGARGLRAPPPPPLLLLLALLPLLPAPGAAAAPAPRPPELQSASAGPSVSLYLSEDEVRRLIGLD
+AELYYVRNDLISHYALSFSLLVPSETNFLHFTWHAKSKVEYKLGFQVDNVLAMDMPQVNISVQGEVPRTLSVFRVELSCT
+GKVDSEVMILMQLNLTVNSSKNFTVLNFKRRKMCYKKLEEVKTSALDKNTSRTIYDPVHAAPTTSTRVFYISVGVCCAVI
+FLVAIILAVLHLHSMKRIELDDSISASSSSQGLSQPSTQTTQYLRADTPNNATPITSSLGYPTLRIEKNDLRSVTLLEAK
+GKVKDIAISRERITLKDVLQEGTFGRIFHGILIDEKDPNKEKQAFVKTVKDQASEIQVTMMLTESCKLRGLHHRNLLPIT
+HVCIEEGEKPMVILPYMNWGNLKLFLRQCKLVEANNPQAISQQDLVHMAIQIACGMSYLARREVIHKDLAARNCVIDDTL
+QVKITDNALSRDLFPMDYHCLGDNENRPVRWMALESLVNNEFSSASDVWAFGVTLWELMTLGQTPYVDIDPFEMAAYLKD
+GYRIAQPINCPDELFAVMACCWALDPEERPKFQQLVQCLTEFHAALGAYV
+```
+
+### Of|1176102141
+```{bash}
+>Of|1176102141 XP_020621816.1| uncharacterized protein LOC110059462 [Orbicella faveolata]
+MAGLEARNFLKVLFLMSVPVLGKCSTKLNVFLDAREVSRFLYDLNTNLFLVQDGVVAPILKTPILSSMIPPIEPYIKDLK
+FKFNATGMVQYSLNFKSSNETIMKHPTANIRLNGLVPRKTKVFRVKFPCTGKVIGGVLLTINISFVDVAGSEIWGPLSLT
+LKRQCVSGNDDLINRYNSTESGEVSPLPAPQICNKRCSKRHVMRRFCLSDFVIKARMESEVMRNGLPRLRLRIARTYKQG
+KVKINNKNQLMEKRGQEITCSCSNLKVNKVYLILGKEDKRKRVLFLDNFSTALEWNKNGKSYVKTFRNRSSCPERKMP
+```
+
+### Ci|198430807
+```{bash}
+>Ci|198430807 ref|XP_002129769.1| PREDICTED: tyrosine-protein kinase RYK [Ciona intestinalis]
+MRVCAYILAVVLLPCMSKCSIDLYLAEDQVEKLFGIADAEMYYIRNGIINENAVNFVAHVQPEHTDLTYLWKVTNKAITV
+AYDLDILDVQKSPAQLNTGSVEMNKHSILYPPKLESKSGTIRYSEDLQPQTLKVSLVCTGEREGNVTVTMKLKLVMDSGT
+DLVVNIKRLKKCLKTHSFVEDKPVLTDQPSEPNDQDLNLGGTQQSTSAFYISVSVVSSFIVLIVVGVTLWHVRMSKRYQR
+SGVDNCIPMQPGAQHLNQFLRPDLPNNALKPPSHSSLMQIITPLINDLGTDINEIQSKLSAIAIPRENVDIGELTLKGTF
+ARIYKGTLDDGTPVLIKTVSDMATEEQKRLLLFESSLLRGMHHRNLLSMKHVVLQDDSTPPMVLFHFMEGGNLKHYLQGL
+KLKESPGLVSGIFGSGSTKYEQVSTQDLVEMAIQIACGMTYLSKRGLVHKDLAARNCVIDRDLKVKISDNALSRDAFPAD
+YCCLGDNENRPVRWLGLESLVHKVYSSASDVWSFGVLLWELQSLAATPYADIDDFEMASYLKDGFRLSQPINCPDHLYSI
+IASCWHYSPDQRPSFTKLLQMLTEFYAELEVYV
+```

### 2021-08-05 MSA_Notum_journey.Rmd
add sequences from the results of tblastn Hs|WIF1 vs sponges

--- 2021-08-04 MSA_Notum_journey.Rmd
@@
 ```
+
+# Search four "representative" proteins that have the WIF domain respect to sponges
+In the tree of WIF from oma.db we can see 4 big clusters that have particular characteristics
+One is the cluster of the Human WIF (HS|WIF1) the the human with RYK domain (Hs|RYK) then those with 
+NTR domain and then those with the "pure"  PK_TYR_SER_THR_PKinase
+We will tblastn from each cluster one and evaluate some of the results
+## The selected sequences:
+
+### Hs|WIF1 
+```{bash}
+>Hs|WIF1 gi|111125011|ref|NP_009122.2| gi|111125011|ref|NP_009122.2| wnt inhibitory factor 1 precursor [Homo sapiens]
+MARRSAFPAAALWLWSILLCLLALRAEAGPPQEESLYLWIDAHQARVLIGFEEDILIVSEGKMAPFTHDFRKAQQRMPAI
+PVNIHSMNFTWQAAGQAEYFYEFLSLRSLDKGIMADPTVNVPLLGTVPHKASVVQVGFPCLGKQDGVAAFEVDVIVMNSE
+GNTILQTPQNAIFFKTCQQAECPGGCRNGGFCNERRICECPDGFHGPHCEKALCTPRCMNGGLCVTPGFCICPPGFYGVN
+CDKANCSTTCFNGGTCFYPGKCICPPGLEGEQCEISKCPQPCRNGGKCIGKSKCKCSKGYQGDLCSKPVCEPGCGAHGTC
+HEPNKCQCQEGWHGRHCNKRYEASLIHALRPAGAQLRQHTPSLKKAEERRDPPESNYIW
+```
+
+### Hs|RYK (picle Rick)
+```{bash}
+>Hs|RYK gi|54607020|ref|NP_001005861.1| gi|54607020|ref|NP_001005861.1| tyrosine-protein kinase RYK isoform 1 precursor [Homo sapiens]
+MRGAARLGRPGRSCLPGARGLRAPPPPPLLLLLALLPLLPAPGAAAAPAPRPPELQSASAGPSVSLYLSEDEVRRLIGLD
+AELYYVRNDLISHYALSFSLLVPSETNFLHFTWHAKSKVEYKLGFQVDNVLAMDMPQVNISVQGEVPRTLSVFRVELSCT
+GKVDSEVMILMQLNLTVNSSKNFTVLNFKRRKMCYKKLEEVKTSALDKNTSRTIYDPVHAAPTTSTRVFYISVGVCCAVI
+FLVAIILAVLHLHSMKRIELDDSISASSSSQGLSQPSTQTTQYLRADTPNNATPITSSLGYPTLRIEKNDLRSVTLLEAK
+GKVKDIAISRERITLKDVLQEGTFGRIFHGILIDEKDPNKEKQAFVKTVKDQASEIQVTMMLTESCKLRGLHHRNLLPIT
+HVCIEEGEKPMVILPYMNWGNLKLFLRQCKLVEANNPQAISQQDLVHMAIQIACGMSYLARREVIHKDLAARNCVIDDTL
+QVKITDNALSRDLFPMDYHCLGDNENRPVRWMALESLVNNEFSSASDVWAFGVTLWELMTLGQTPYVDIDPFEMAAYLKD
+GYRIAQPINCPDELFAVMACCWALDPEERPKFQQLVQCLTEFHAALGAYV
+```
+
+### Of|1176102141
+```{bash}
+>Of|1176102141 XP_020621816.1| uncharacterized protein LOC110059462 [Orbicella faveolata]
+MAGLEARNFLKVLFLMSVPVLGKCSTKLNVFLDAREVSRFLYDLNTNLFLVQDGVVAPILKTPILSSMIPPIEPYIKDLK
+FKFNATGMVQYSLNFKSSNETIMKHPTANIRLNGLVPRKTKVFRVKFPCTGKVIGGVLLTINISFVDVAGSEIWGPLSLT
+LKRQCVSGNDDLINRYNSTESGEVSPLPAPQICNKRCSKRHVMRRFCLSDFVIKARMESEVMRNGLPRLRLRIARTYKQG
+KVKINNKNQLMEKRGQEITCSCSNLKVNKVYLILGKEDKRKRVLFLDNFSTALEWNKNGKSYVKTFRNRSSCPERKMP
+```
+
+### Ci|198430807
+```{bash}
+>Ci|198430807 ref|XP_002129769.1| PREDICTED: tyrosine-protein kinase RYK [Ciona intestinalis]
+MRVCAYILAVVLLPCMSKCSIDLYLAEDQVEKLFGIADAEMYYIRNGIINENAVNFVAHVQPEHTDLTYLWKVTNKAITV
+AYDLDILDVQKSPAQLNTGSVEMNKHSILYPPKLESKSGTIRYSEDLQPQTLKVSLVCTGEREGNVTVTMKLKLVMDSGT
+DLVVNIKRLKKCLKTHSFVEDKPVLTDQPSEPNDQDLNLGGTQQSTSAFYISVSVVSSFIVLIVVGVTLWHVRMSKRYQR
+SGVDNCIPMQPGAQHLNQFLRPDLPNNALKPPSHSSLMQIITPLINDLGTDINEIQSKLSAIAIPRENVDIGELTLKGTF
+ARIYKGTLDDGTPVLIKTVSDMATEEQKRLLLFESSLLRGMHHRNLLSMKHVVLQDDSTPPMVLFHFMEGGNLKHYLQGL
+KLKESPGLVSGIFGSGSTKYEQVSTQDLVEMAIQIACGMTYLSKRGLVHKDLAARNCVIDRDLKVKISDNALSRDAFPAD
+YCCLGDNENRPVRWLGLESLVHKVYSSASDVWSFGVLLWELQSLAATPYADIDDFEMASYLKDGFRLSQPINCPDHLYSI
+IASCWHYSPDQRPSFTKLLQMLTEFYAELEVYV
+```
+## Results:
+### Hs|WIF1 vs Halisarca caerulea comp25790_c0_seq1 transcribed RNA sequence
+```{bash}
+>Hc|comp25790
+CQRAECIPGCLNGGTCAGPNWCRCARGWSGNRCRRAVCIPACNNGGKCTAPNTCECAEGWTGNQCQRPVCDSECLNGGIC
+AAPNTCQCSSGWSGDHCDLPVCRPKCTNGGICIRPSKCLCDSSWTGKRCQKPVCRPGCENGGTCTEPNTCQCTSGWSGDR
+C
+```
+### Hs|WIF1 vs Halichondria panicea TRINITY_DN792_c2_g1_i4, transcribed RNA sequence
+```{bash}
+>Hp|TRINITY_DN792_c2_g1_i4
+CENGGICTQERTCHCAPGYEGPLCEEAVCFPPCTNGGNCTAPGFCECPREWEGIRCEDPGCSPSCENGGTCIRPGECYCT
+PQWTGDNCQDAICNPPCGNGGHCISPGHCECGGTGFLGSRCTEAVCKPACENGGECVEPNVCQCLSLWTGNYCDT
+```
+### Hs|WIF1 vs Aplysina aerophoba TR173969_c0_g2_i1 transcribed RNA sequence
+```{bash}
+>Ae|TR173969_c0_g2_i1
+RRCRKAICNEPCRNGGTCTAPNVCACADGYMGQLCEVPVCSRECQNGGICIGKDECQCEMGYSGLHCESAICTDSCMNGG
+TCVEPETCTCPANYTGRVCSEPVCIRPCLNVGQCTGPGVCTCTAEFTGDLCEVPICLDPCLNGGYCSAPNVCTCEDGYEG
+HNC
+```
+### Hs|WIF1 vs Leucetta chagosensis breed sponge isolate calcarea TRINITY_DN9568_c1_g1_i1, transcribed RNA sequence
+```{bash}
+>Lc|TRINITY_DN9568_c1_g1_i1
+PKSAWTGSRCQTPVCLPSCQNGGQCVSPQTCSCAAGYTGSSCGNAVCSTSCKNGGSCVSPNKCSCPAGYTGSYCEKAVCS
+TSCRNGGSCVRPNTCSCPAGYTGSYCEKAVCSTSCQNGGSCVRPNTCSCPAGYTGSYCEKAVCSTSCKNGGSCVSPNTCS
+CPAGYTGSYCEK
+```
+
+```{bash}
+hmmpress my_data/pfam/Pfam-A.hmm
+
+hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_HS_WIF1vssponges_domtbl.out my_data/pfam/Pfam-A.hmm my_data/Hs_WIF1vs_sponges.fasta > /dev/null
+```
+
+## Import hmmscan of WIF1 vs sponges results into R
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target_1",
+                        "description_of_target_2","description_of_target_3")
+
+WIF_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_profile_HS_WIF1vssponges_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_hmmscan)[1:25] <- second_line_fields
+
+WIF_hmmscan %>% 
+  distinct(target_name, query_name) %>% 
+  pivot_wider(names_from = target_name, values_from = target_name,values_fill = "0") %>% 
+  unite(col = "domains",2:11) %>% 
+  mutate(domains = domains %>% str_remove_all("0_") %>% str_remove_all("_0"),
+         query_name = query_name %>% str_replace("\\|","_")) %>% 
+  unite(query_name, 1:2, sep = "__DOMAIN__") %>% view()
+```

### 2021-08-06 MSA_Notum_journey.Rmd
add the sequences and the results for sponges

@@
 ```
+
+### Hs|RYK vs Halichondria panicea TRINITY_DN396839_c0_g1_i1, transcribed RNA sequence
+```{bash}
+>Hp|TRINITY_DN396839_c0_g1_i1
+ESCLMKGFCHQNVNPILGACMENEKQPLLVYAYSTEGNLKKFLQRCKMSEMASSYALSTQQLVYIAIQIIRGVQYLHRKR
+VVHRDVATRNCVIDHQLNVKVTDTALSRDLFPNDYHCLGDNENRPVKWLAIEALLDRHFTPASDVWSFGVTMWELMTLGQ
+QPYADVDPFEMATYLKEGYRIAQPINCPDELFSVMACCWSMLGEERPKLTQLQACLQDFYTALGRFI
+```
+
+### Hs|RYK vs Cymbastela stipitata TRINITY_DN14054_c0_g1_i1, transcribed RNA sequence
+```{bash}
+>Cs|TRINITY_DN14054_c0_g1_i1
+NIASVGAVATTDFSISFPCTNTLQGRADVRVTLNFTFDFTGGTLRSLVGQVFTMTGTRVCNCTNSRCDNTEPPNDGGVNN
+EIFYIVIGCVGGVILLVIMVTVLYHCIMLGMWVKRRSQDEEPLPNIEDVIPMPPYPMVTITPLSSQVPIAPLPNSPRNSF
+SVPSDLSKSLRSLQSFKDLIVDRKRISIGQVLKEGVFGVMYDGYLSNAEDDVEGAIPVIIKTVKDNTPDIVVKSLLEGGG
+ATRAVSHRHVLPLLAAHVSDTEQPMLLFPKTSLGTLKGLLMRCREPKRGVSLTLTTQNLVFIAGQISRGMYHLTRKGLIH
+RDLAARNIYVHENLHVKIGDRGLSWDLFPSEYSRLPDGEMCPIRWMSAEVLSERKYSHYSDVWSFGVVLWELMTLGRIPY
+EEVPAEDMLAMLTAGHRLSQPKNCPDELFVLMGWCWALTPTDRPRFSHLTLRLKEFHEKINAFV
+```
+
+### Hs|RYK vs Neopetrosia compacta breed sponge isolate demosponge TRINITY_DN1516_c3_g1_i2, transcribed RNA sequence
+```{bash}
+>Nc|TRINITY_DN1516_c3_g1_i2
+RDVFVDRKRIQFGCKITEGVFGVMYDGYLTNAEDDVEGAVPVIIKTVKDNTPDVVVKSLLEGGSATRGVSHRHLLPLLAA
+HASDLEQPMLLFPKTAHGSLKSLLLCSRGAQRVIPGSPFLTTQDLVFMAEQVARGMYHLTRKGLVHKDLAARNIYVHENL
+HVKIGDRGLCWDFFPSEYSTLEGDQELIASPIRWMAAEVIAEKKYSHYSDVWAFGVVLWEIMTKGKIPYEDVLPEQMYSY
+LTYGSRLQQPKNCPDDLFSLMGWCWALTPGDRPRFSHLTIRLKEFHERLGAFI
+```
+
+### Hs|RYK vs Dysidea avara TR158463_c0_g1_i1 transcribed RNA sequence
+```{bash}
+>Da|TR158463_c0_g1_i1
+MKDILVDKNRIQLGELIKEGTYGRMYEGYLANTEDDVEGSVSIIVKTVSDITPDQVVASLVDGCLVLRHIQHRHILQALG
+VYSNEQEPVMVLLARTTFGTLKQFLDDIRLQGGPQSSYGKLLLTQDMVFISAQIARGMYHLSRKGGIIHKDLAARNIYIH
+ENLHVKIGDRGLSWDFYPDDYQVTPNGEYVPVKWASVEVLEEQQYSMYSDVWAFGVVLWEIMTVGLVPYDSVTPNELVDY
+LKSGQRLTRPTNCPDDMFSIMGQCWALTPTDRPKFSHLTVGLDHFHLRLNSYI
+```
+
+```{bash}
+hmmpress my_data/pfam/Pfam-A.hmm
+
+hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_HS_RYKvssponges_domtbl.out my_data/pfam/Pfam-A.hmm my_data/Hs_RYKvs_sponges.fasta > /dev/null
+```
+
+## Import hmmscan of WIF1 vs sponges results into R
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target_1",
+                        "description_of_target_2","description_of_target_3")
+
+WIF_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_profile_HS_RYKvssponges_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_hmmscan)[1:25] <- second_line_fields
+
+WIF_hmmscan %>% 
+  distinct(target_name, query_name) %>% 
+  pivot_wider(names_from = target_name, values_from = target_name,values_fill = "0") %>% 
+  unite(col = "domains",2:11) %>% 
+  mutate(domains = domains %>% str_remove_all("0_") %>% str_remove_all("_0"),
+         query_name = query_name %>% str_replace("\\|","_")) %>% 
+  unite(query_name, 1:2, sep = "__DOMAIN__") %>% view()
+```
+
+About Of|1176102141 we got only one result:
+### Of|1176102141 vs Cymbastela stipitata TRINITY_DN17682_c0_g1_i1, transcribed RNA sequence
+```{bash}
+>Cs|TRINITY_DN17682_c0_g1_i1
+LPPLPSSVDEISISWHASEEVIYELHVGQDPQGVFEDPRLNIPENGTIPRNKTAFSISFPC
+```
+
+```{bash}
+touch my_data/Of1176102141_vs_sponges.fasta
+
+hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_Of1176102141vssponges_domtbl.out my_data/pfam/Pfam-A.hmm my_data/Of1176102141_vs_sponges.fasta > /dev/null
+```
+
+## Import hmmscan of WIF1 vs sponges results into R
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target_1",
+                        "description_of_target_2","description_of_target_3")
+
+WIF_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_profile_Of1176102141vssponges_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_hmmscan)[1:25] <- second_line_fields
+
+WIF_hmmscan %>% 
+  distinct(target_name, query_name) %>% 
+  pivot_wider(names_from = target_name, values_from = target_name,values_fill = "0") %>% 
+  unite(col = "domains",2:11) %>% 
+  mutate(domains = domains %>% str_remove_all("0_") %>% str_remove_all("_0"),
+         query_name = query_name %>% str_replace("\\|","_")) %>% 
+  unite(query_name, 1:2, sep = "__DOMAIN__") %>% view()
+```
+
+### Ci|198430807 vs Halichondria panicea TRINITY_DN396839_c0_g1_i1, transcribed RNA sequence
+```{bash}
+>Hp|TRINITY_DN396839_c0_g1_i1
+ESCLMKGFCHQNVNPILGACMENEKQPLLVYAYSTEGNLKKFLQRCKMSEMASSYALSTQQLVYIAIQIIRGVQYLHRKR
+VVHRDVATRNCVIDHQLNVKVTDTALSRDLFPNDYHCLGDNENRPVKWLAIEALLDRHFTPASDVWSFGVTMWELMTLGQ
+QPYADVDPFEMATYLKEGYRIAQPINCPDELFSVMACCWSMLGEERPKLTQLQACLQDFYTALGRFI
+```
+
+### Ci|198430807 vs Cymbastela stipitata TRINITY_DN14054_c0_g1_i1, transcribed RNA sequence
+```{bash}
+>Cs|TRINITY_DN14054_c0_g1_i1
+LCLRAVWVLLALYRCVCALDWFIPAAEVQRIEGEENAPALYLVRQSVVQRSTLPLSETAMNTRVMFSWAGSGLAYQFKSV
+SSNPAVLMGAEFENIASVGAVATTDFSISFPCTNTLQGRADVRVTLNFTFDFTGGTLRSLVGQVFTMTGTRVCNCTNSRC
+DNTEPPNDGGVNNEIFYIVIGCVGGVILLVIMVTVLYHCIMLGMWVKRRSQDEEPLPNIEDVIPMPPYPMVTITPLSSQV
+PIAPLPNSPRNSFSVPSDLSKSLRSLQSFKDLIVDRKRISIGQVLKEGVFGVMYDGYLSNAEDDVEGAIPVIIKTVKDNT
+PDIVVKSLLEGGGATRAVSHRHVLPLLAAHVSDTEQPMLLFPKTSLGTLKGLLMRCREPKRGVSLTLTTQNLVFIAGQIS
+RGMYHLTRKGLIHRDLAARNIYVHENLHVKIGDRGLSWDLFPSEYSRLPDGEMCPIRWMSAEVLSERKYSHYSDVWSFGV
+VLWELMTLGRIPYEEVPAEDMLAMLTAGHRLSQPKNCPDELFVLMGWCWALTPTDRPRFSHLTLRLKEFHEKINAFV
+```
+
+### Ci|198430807 vs Halichondria panicea TRINITY_DN874_c0_g1_i3, transcribed RNA sequence
+```{bash}
+>Hp|TRINITY_DN874_c0_g1_i3
+LTTDMPVSDLKSSPRHSHSSISVPPALNNSLRNLHSFRDLFVHRKRISIGVVLTEGVFGVIYDGYLSNAEDDVEGVTPVI
+IKTVKDNTPEIVVRSLLEGGAALRHVPHRHLLPLLACHASDSEQPMLLFPKTALGTLKTVLLRTRDNKTTPGGSQKGALA
+LSTQNLVMVAAQISRGMYHLTKKGLTHRDLAARNIYIHQNLHVRIGDRGLSWDLYPEEYSQMPDGEMCPVKWMAAEVLTD
+RNYSHYSDVWSFGVVLWEIMTLGKIPYSENTAEEMVALLTAGQRLSQPKNCPDDLFVLMGWCWALTPTDRPRFSHLTLRL
+KEFHEKICSFV
+```
+
+### Ci|198430807 vs Dysidea avara TR158463_c0_g1_i1 transcribed RNA sequence
+```{bash}
+>Da|TR158463_c0_g1_i1
+SLKPAVDGSLAVLTAELNKSVHSLFSMKDILVDKNRIQLGELIKEGTYGRMYEGYLANTEDDVEGSVSIIVKTVSDITP
+DQVVASLVDGCLVLRHIQHRHILQALGVYSNEQEPVMVLLARTTFGTLKQFLDDIRLQGGPQSSYGKLLLTQDMVFISAQ
+IARGMYHLSRKGGIIHKDLAARNIYIHENLHVKIGDRGLSWDFYPDDYQVTPNGEYVPVKWASVEVLEEQQYSMYSDVWA
+FGVVLWEIMTVGLVPYDSVTPNELVDYLKSGQRLTRPTNCPDDMFSIMGQCWALTPTDRPKFSHLTVGLDHFHLRLNSYI
+```
+
+```{bash}
+touch my_data/Ci_198430807_vs_sponges.fasta
+
+hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_profile_Ci_198430807vssponges_domtbl.out my_data/pfam/Pfam-A.hmm my_data/Ci_198430807_vs_sponges.fasta > /dev/null
+```
+
+## Import hmmscan of WIF1 vs sponges results into R
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target_1",
+                        "description_of_target_2","description_of_target_3")
+
+WIF_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_profile_Ci_198430807vssponges_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_hmmscan)[1:25] <- second_line_fields
+
+WIF_hmmscan %>% 
+  distinct(target_name, query_name) %>% 
+  pivot_wider(names_from = target_name, values_from = target_name,values_fill = "0") %>% 
+  unite(col = "domains",2:11) %>% 
+  mutate(domains = domains %>% str_remove_all("0_") %>% str_remove_all("_0"),
+         query_name = query_name %>% str_replace("\\|","_")) %>% 
+  unite(query_name, 1:2, sep = "__DOMAIN__") %>% view()
+```

### 2021-08-06 MSA_Notum_journey.Rmd
add sponge sequences and make a new WIF tree

@@
 
-# hmmbuild
-```{bash}
-hmmbuild --amino --cpu 4  my_data/NOTUM_try my_data/hmmsearch_env_coord_msa_muscle.fa 
-hmmbuild --amino --cpu 4  my_data/WIF_try my_data/WIF_hmmsearch_env_coord_msa_muscle.fa 
-hmmbuild --amino --cpu 4  my_data/wnt_try my_data/wnt_hmmsearch_env_coord_msa_muscle.fa 
-```
-
 # hmmscan WIF proteins in pfam domains
@@
 ```
+
 ## Import hmmscan results into R
@@
 ```
+
+# Remake the WIF tree
+We will use some sequences from sponges with the previous sequences
+
+## import the new sequences
+```{r}
+seq_sponges <- readAAStringSet("WIF_sponge.fasta")
+```
+
+## Import hmmsearch results into R
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target")
+
+WIF_hmmsearch <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=23;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_hmmsearch)[1:23] <- second_line_fields
+```
+
+## Get only the filtered sequences 
+```{r}
+# filter for the hmmsearch env_coord sequences
+fasta_db_fil_with_len <- fasta_db[names_fst_db %in% WIF_hmmsearch$target_name]
+
+WIF_hmmsearch <- WIF_hmmsearch %>% 
+  filter(!duplicated(target_name)) %>% 
+  select(target_name, from_env_coord, to_env_coord) %>% 
+  arrange(target_name)
+
+identical(fasta_db_fil_with_len %>% names %>% str_remove(" .+"),
+          WIF_hmmsearch$target_name)
+
+fasta_db_fil_with_len <- pmap(list(fasta_db_fil_with_len %>% as.list, 
+          WIF_hmmsearch %>% select(target_name, from_env_coord) %>% deframe %>% as.list(),
+          WIF_hmmsearch %>% select(target_name, to_env_coord) %>% deframe %>% as.list()),
+     subseq) %>% Biostrings::AAStringSet()
+
+# cat the two files
+fasta_db_fil_with_len_sponges <- c(fasta_db_fil_with_len,seq_sponges) %>% 
+  writeXStringSet("WIF_and_sponges_sequences.fasta")
+```
+
+## perform Multiple Sequence Alignment with MUSCLE hmmsearch
+```{r}
+## env_coord
+hmmsearch_env_coord_muscle <- msaMuscle(fasta_db_fil_with_len_sponges, type = "protein")
+hmmsearch_env_coord_bio2mds <- msa::msaConvert(hmmsearch_env_coord_muscle, type = "bios2mds::align")
+export.fasta(hmmsearch_env_coord_bio2mds, outfile = "WIFtree_withsponges_hmmsearch_env_coord_msa_muscle.fa", ncol = 60, open = "w")
+```
+
+## IQTREE hmmsearch
+```{bash}
+docker run --rm -ti -v $(pwd):/home/my_data staphb/iqtree
+
+cd home
+
+iqtree -s my_data/WIFtree_withsponges_hmmsearch_env_coord_msa_muscle.fa -nt 4 -mset LG -pre my_data/my_hmmsearch_tree/WIFtree_withsponges_hmmsearch_env_coord_tree
+```
+
+## search which domains these sponges sequences have
+```{bash}
+hmmscan --cut_ga --domtblout my_data/hmm_search/Sponges_domains_domtbl.out my_data/pfam/Pfam-A.hmm my_data/WIF_sponge.fasta > /dev/null
+```
+
+```{bash}
+hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_Sponges_domains_domtbl.out my_data/pfam/Pfam-A.hmm my_data/WIF_and_sponges_sequences.fasta > /dev/null
+```
+
+## Import the hmmscan with the domains
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target_1",
+                        "description_of_target_2","description_of_target_3")
+
+WIF_sponges_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_Sponges_domains_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_sponges_hmmscan)[1:25] <- second_line_fields
+
+WIF_sponges_hmmscan %>% 
+  distinct(target_name, query_name) %>% 
+  pivot_wider(names_from = target_name, values_from = target_name,values_fill = "0") %>% 
+  unite(col = "domains",2:4) %>% 
+  mutate(domains = domains %>% str_remove_all("0_") %>% str_remove_all("_0"),
+         query_name = query_name %>% str_replace("\\|","_")) %>% 
+  mutate(query_name_1 = query_name) %>% 
+  unite(query_name, 1:2, sep = "__DOMAIN__") %>% view()
+```

### 2021-08-06 MSA_Notum_journey.Rmd
change the names of the sequences adding the domains for the tree

--- 2021-08-06 MSA_Notum_journey.Rmd
@@
 ```
+
+# Remake the WIF tree
+We will use some sequences from sponges with the previous sequences
+
+## import the  sequences
+```{r}
+suppressPackageStartupMessages({
+library(Biostrings)
+  })
+# import the oma_db first (we will filter it after)
+fasta_db <- readAAStringSet("oma_db")
+fasta_db <- fasta_db[sort(names(fasta_db))]
+
+names_fst_db <- fasta_db  %>% names %>% str_remove(" .+")
+
+# import the sponges
+seq_sponges <- readAAStringSet("WIF_sponge.fasta")
+```
+
+## Import hmmsearch results into R
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target")
+
+WIF_hmmsearch <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=23;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_hmmsearch)[1:23] <- second_line_fields
+```
+
+## Get only the filtered sequences 
+```{r}
+# filter for the hmmsearch env_coord sequences
+fasta_db_fil_with_len <- fasta_db[names_fst_db %in% WIF_hmmsearch$target_name]
+
+# cat the two files
+fasta_db_fil_with_len_sponges <- c(fasta_db_fil_with_len,seq_sponges) %>% 
+  writeXStringSet("WIF_complete_seq_and_sponges_sequences.fasta")
+```
+
+## find domains in order to properly rename the sequences
+### search the domains
+```{bash}
+hmmscan --cut_ga --domtblout my_data/hmm_search/WIF_Sponges_domains_domtbl.out my_data/pfam/Pfam-A.hmm my_data/WIF_complete_seq_and_sponges_sequences.fasta > /dev/null
+```
+
+### Import the hmmscan with the domains
+```{r}
+second_line_fields <- c("target_name", "accession_1", "tlen", "query_name",
+                        "accession_2", "qlen",   "E-value_full_seq", "score_full_seq",
+                        "bias_full_seq",
+                        "this_domain_#",  "of_this_domain",  "c-Evalue_this_domain",
+                        "i-Evalue_this_domain",  "score_this_domain", "bias_this_domain", 
+                        "from_hmm_coord", "to_hmm_coord", "from_ali_coord", "to_ali_coord", 
+                        "from_env_coord", "to_env_coord", "acc", "description_of_target_1",
+                        "description_of_target_2","description_of_target_3")
+
+WIF_sponges_hmmscan <- data.table::fread(cmd = "grep -v '^#' hmm_search/WIF_Sponges_domains_domtbl.out | awk -v OFS='\t'  '{for(i=1;i<=29;i++) printf $i\"\t\"; print \"\"}'",  header = FALSE, sep = "\t",  fill=TRUE)
+
+names(WIF_sponges_hmmscan)[1:25] <- second_line_fields
+```
+
+### change the names 
+```{r}
+new_names <- WIF_sponges_hmmscan %>% 
+  distinct(target_name, query_name) %>% 
+  pivot_wider(names_from = target_name, values_from = target_name,values_fill = "0") %>% 
+  unite(col = "domains",2:11) %>% 
+  mutate(domains = domains %>% str_remove_all("0_") %>% str_remove_all("_0"),
+         query_name = query_name %>% str_replace("\\|","_")) %>% 
+  mutate(query_name_1 = query_name) %>% 
+  unite(query_name, 1:2, sep = "__DOMAIN__")
+
+identical(str_remove(names(fasta_db_fil_with_len_sponges)," .+") %>% str_replace("\\|","_"),new_names$query_name_1)
+
+names(fasta_db_fil_with_len_sponges) <- new_names$query_name
+```
+
+## perform Multiple Sequence Alignment with MUSCLE hmmsearch
+```{r}
+## env_coord
+hmmsearch_env_coord_muscle <- msaMuscle(fasta_db_fil_with_len_sponges, type = "protein")
+
+hmmsearch_env_coord_bio2mds <- msa::msaConvert(hmmsearch_env_coord_muscle, type = "bios2mds::align")
+export.fasta(hmmsearch_env_coord_bio2mds, outfile = "WIFtree_withsponges_hmmsearch_env_coord_msa_muscle.fa", ncol = 60, open = "w")
+```
+
+## IQTREE hmmsearch
+```{bash}
+docker run --rm -ti -v $(pwd):/home/my_data staphb/iqtree
+
+cd home
+
+iqtree -s my_data/WIFtree_withsponges_hmmsearch_env_coord_msa_muscle.fa -nt 4 -mset LG -pre my_data/my_hmmsearch_tree/WIFtree_withsponges_hmmsearch_env_coord_tree
+```
+
+## search which domains these sponges sequences have against pfam
+```{bash}
+hmmscan --cut_ga --domtblout my_data/hmm_search/Sponges_domains_domtbl.out my_data/pfam/Pfam-A.hmm my_data/WIF_sponge.fasta > /dev/null
+```
